Gaia identifies VFTS682 as the most massive runaway star known to date

### 2018-05-11 VFTS682.tex
added joachim and minor

\documentclass[apjl,twocolumn]{emulateapj}
\usepackage{graphicx}
\usepackage[varg]{txfonts}
\usepackage[pagebackref,breaklinks,colorlinks,citecolor=blue]{hyperref}        
\renewcommand*{\backref}[1]{[#1]}  % gives neat back references in the pdf
%\usepackage[%draft, 
%colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue]{hyperref}
\usepackage{aas_macros}
%\usepackage{amsmath} % clashes with emulateapjj for some reaons
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{comment}
\usepackage{multirow}
%\usepackage{chngpage}
%\usepackage{lscape}
\usepackage{url}
\newcommand{\todo}[1]{{\large $\blacksquare$~\textbf{\color{red}[#1]}}~$\blacksquare$}
\newcommand{\udef}{\stackrel{\mathrm{def}}{=}}
% for tree diagram
%\usepackage{forest}
%\usepackage{tikz-qtree}
%\usetikzlibrary{shadows,trees}

@@

\author{M.~Renzo$^{1}$, S.~E.~de~Mink$^{1}$, D.~J.~Lennon$^{2}$,
  S.~Justham$^{3,4}$, J.~Vink$^{5}$, F.~R.~Schneider$^6$,
  J.~Bestenlehner, A.~de~Koter$^{1}$ \todo{... add coauthors...} }

\affil{$^{1}$Astronomical Institute Anton Pannekoek, University of
    Amsterdam, 1098 XH Amsterdam, The Netherlands \\
    $^{2}$ ESA, European Space Astronomy Centre, Apdo. de Correos 78, E-28691 Villanueva de la Ca\~nada, Madrid, Spain \\
    $^{3}$ {School of Astronomy \& Space Science, University of the Chinese
    Academy of Sciences, Beijing 100012, China}\\
     $^4$ {National Astronomical Observatories, Chinese Academy of
       Sciences, Beijing 100012, China}\\
     $^5$ {Armagh Observatory, College Hill, Armagh BT61 9DG, UK}\\
     $^6$ {Department of Physics, University of Oxford, Keble Road, Oxford OX1 3RH, UK}  
}

@@

The star VFTS682  \citep{evans:11}, located at right ascension (RA)
05$^\mathrm{h}$38$^\mathrm{m}$55.510$^\mathrm{s}$  and declination
(DEC) -69:04:26.72 in the ICGS frame \citep[][]{brown:18}
was originally classified as a young stellar object \citep{gruendl:09}
based on its mid-infrared excess.  \citet{evans:11} classified the
object as Wolf-Rayet star of spectral type WNh5 using spectra from the
VFTS survey.  The spectra available covered $\lambda$4000--7000 and
were taken at multiple epochs. Using the same dataset,
\citet{bestenlehner:11} excluded the presence of a close companion
with high confidence from the absence of radial velocity variations.

@@

These can be converted in the
the components of the relative transverse velocity $\delta v_\mathrm{RA}=38\pm17\,\kms$,
$\delta v_\mathrm{DEC}=26\pm19\,\kms$, assuming a distance of
50\,kpc. % (we do not account for the uncertainty in the distance
% estimate when propagating errors).
The radial velocity from
\cite{bestenlehner:11} then gives the third component along
the line of sight, allowing us to calculate the three-dimensional
peculiar speed of the star:

>>>>

\documentclass[apjl,twocolumn]{emulateapj}
\usepackage{graphicx}
\usepackage[varg]{txfonts}
%\usepackage[pagebackref,breaklinks,colorlinks,citecolor=blue]{hyperref}        
\usepackage[%draft, 
pagebackref,colorlinks,citecolor=blue,linkcolor=blue,urlcolor=blue]{hyperref}
\renewcommand*{\backref}[1]{[#1]}  % gives neat back references in the pdf
\usepackage{aas_macros}
%\usepackage{amsmath} % clashes with emulateapjj for some reaons
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{comment}
\usepackage{multirow}
%\usepackage{chngpage}
%\usepackage{lscape}
\usepackage{url}
\newcommand{\todo}[1]{{\large $\blacksquare$~\textbf{\color{red}[#1]}}~$\blacksquare$}
\newcommand{\udef}{\stackrel{\mathrm{def}}{=}}
% for tree diagram
%\usepackage{forest}
%\usepackage{tikz-qtree}
%\usetikzlibrary{shadows,trees}

@@

\author{M.~Renzo$^{1}$, S.~E.~de~Mink$^{1}$, D.~J.~Lennon$^{2}$,
  S.~Justham$^{3,4}$, J.~Vink$^{5}$, F.~R.~Schneider$^6$,
  J.~Bestenlehner$^7$, A.~de~Koter$^{1}$}

\affil{$^{1}$Astronomical Institute Anton Pannekoek, University of
    Amsterdam, 1098 XH Amsterdam, The Netherlands \\
    $^{2}$ ESA, European Space Astronomy Centre, Apdo. de Correos 78, E-28691 Villanueva de la Ca\~nada, Madrid, Spain \\
    $^{3}$ {School of Astronomy \& Space Science, University of the Chinese
    Academy of Sciences, Beijing 100012, China}\\
     $^4$ {National Astronomical Observatories, Chinese Academy of
       Sciences, Beijing 100012, China}\\
     $^5$ {Armagh Observatory, College Hill, Armagh BT61 9DG, UK}\\
     $^6$ {Department of Physics, University of Oxford, Keble Road,
       Oxford OX1 3RH, UK} \\
     $^7$ {Department of Physics and Astronomy, Hicks Building, Hounsfield Road, University of Sheffield, Sheffield S3 7RH, UK}
}

@@

The star VFTS682  \citep{evans:11}, located at right ascension (RA)
05$^\mathrm{h}$38$^\mathrm{m}$55.510$^\mathrm{s}$  and declination
(DEC) -69:04:26.72 in the ICGS frame \todo{check coordinates} \citep[][]{brown:18}
was originally classified as a young stellar object \citep{gruendl:09}
based on its mid-infrared excess.  \citet{evans:11} classified the
object as Wolf-Rayet star of spectral type WNh5 using spectra from the
VFTS survey.  The spectra available covered $\lambda$4000--7000 and
were taken at multiple epochs. Using the same dataset,
\citet{bestenlehner:11} excluded the presence of a close companion
with high confidence from the absence of radial velocity variations.

@@

These can be converted in the
the components of the relative transverse velocity $\delta v_\mathrm{RA}=38\pm17\,\kms$,
$\delta v_\mathrm{DEC}=26\pm19\,\kms$, assuming a distance of
50\,kpc. % (we do not account for the uncertainty in the distance
% estimate when propagating errors).
The radial velocity from
\cite{bestenlehner:11} then gives the third component along
the line of sight, allowing us to calculate the three-dimensional
peculiar speed of the star\footnote{We implicitly assume that the use
  of a different reference frame for $\delta v_\mathrm{rad}$ does not
  introduce significant errors.}:
